Predicting Diabetes Based on Various Factors Using Machine Learning Models

### 2023-12-13 manuscript/manuscript.tex
grammar edits
Results section edits

  \begin{figure}[tbp]
      \centering
      \caption{Confusion Matrix Heatmap}
      \includegraphics[width=\textwidth]{Confusion Matrix Heatmap}
      \label{fig:Heatmap}
      \end{figure}

  \begin{figure}[tbp]
    \centering
    \caption{Variance Importance Plot}
    \includegraphics[width=\textwidth]{Variance Importance}
    \label{fig:importance}
  \end{figure}

@@

After completing our methods section, we can now move on to talk about the results of our model. Based on our logistic regression model, 
we now know that all of the predictors in the data set except skin thickness are important in order to predict whether a patient may have 
diabetes or not. With this information medical professionals will be able to ensure proper treatment to patients as they can use these 
predictors in order to tell if a patient may have diabetes even sooner than typical means. The model allows for medical professionals to 
use the model in order to further their research into diabetes and the various precursors.

>>>>

  \begin{figure}[tbp]
      \centering
      \caption{Confusion Matrix Heatmap}
      \includegraphics[width=\textwidth]{Confusion Matrix Heatmap.pdf}
      \label{fig:Heatmap}
      \end{figure}

  \begin{figure}[tbp]
    \centering
    \caption{Variance Importance Plot}
    \includegraphics[width=\textwidth]{Variance Important.pdf}
    \label{fig:importance}
  \end{figure}

@@

After completing our methods section, we can now move on to talk about the results of our model. Based on Figure~ref{fig:importance}, we can 
see that the top three predictors are glucose, BMI, and age. The result of glucose being of the greatest importance makes complete sense with 
medical knowledge of diabetes as a patient that has high amounts of glucose in their bloodstream could have type 2 diabetes. This is known due
to glucose not being absorbed by insulin as these patients do not use insulin properly. We can see that almost all of the outcomes are explained
by glucose. The next predictor that is successful in predicting a large amount of the data is the patients BMI. This alligns on a medical standpoint
as patients who have larger BMI values are more susceptable to getting type 2 diabetes as they are considered to be obese. Based on our results, BMI
was able to predict about half of the outcomes. The last predictor that proved to be valuable in predicting if someone has diabetes is age. This result
is somewhat medically backed but not entirely a result that we expected. Often times people that are older have diabetes due to numerous factors but it is 
not as common for younger folks.
